|                          |
|--------------------------|
| title: "Simple document" |
| output: "html_document"  |

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

I'm an R Markdown document!

# Section 1

Here's a **code chunk** that samples from a *normal distribution*:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too! The mean is `r round(mean(samp), 2)`.

# Section 3

### Plot from last time

This is going to make a plot! First I generate a data frame then use `ggplot` to create a scatterplot.

```{r chunk_scatterplot, echo = FALSE}
plot_df = 
  tibble(
  x = rnorm(n = 1000),
  y = 1 + 2 * x + rnorm(n = 1000)
)

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

# Section 4

This is the learning assessment in the P8105 R Markdown formatting section. This is going to create a data frame and use ggplot to make a histogram.

```{r}
la_df = 
    tibble(
        norm = rnorm(n = 500, mean = 1),
        logical = norm > 0,
        abs_norm = abs(norm)
    )

ggplot(la_df, aes(x = abs_norm)) + geom_histogram()
```



